\textbf{CMCS 818J Project Final Report}

### 2012-12-19 doc/final_report/draft_report.tex
Added to Looking Forward section.

\section{ Benchmarking }

@@

	We ran some preliminary calculations to ballpark the size of L and R the public key of the SADS scheme.
	Recall, L and R are two matrices having elements in Z q, where q is derived from the security parameter k and the upper bound on the size of the stream, n.
	So a rough estimate of the size of L and R would be the size of the matrices, (ie. the number of elements) multiplied by the amount of space required for each element.
	Below is a table of these preliminary calculations.

@@

	\subsection{Production Quality Libraries}
	It is yet to be seen whether the existing Ruby matrix libraries, either the built in or SciRuby, 
	will be sufficiently efficient for the needs of the SADS scheme. That's not to say the current 
	choices of technologies will not produce production quality code but, as mentioned earlier, we have
	been investigating some optimized libraries listed here.

	\begin{enumerate}
	\item \textbf{NTL 5.5.2} : A free software written in C++ providing data structures and algorithms for arbitrary length integers, for vectors, matrices and polynomials over the integers and over the finite fields and for arbitrary precision floating point arithmetic. \texttt{http://shoup.net/ntl/}
	\item \textbf{MAGMA V2.18} : The kernel of Magma contains implementations of many of the important concrete classes of structure in five fundamental branches of algebra, namely group theory, ring theory, field theory, module theory and the theory of algebras.
	In addition, certain families of structures from algebraic geometry and finite incidence geometry are included. \texttt{http://magma.maths.usyd.edu.au/}
	\end{enumerate}

>>>>

	\subsection{ Benchmarking }

@@

	We ran some preliminary calculations to ballpark the size of matrices L and R, the public key of the SADS scheme.
	Recall that L and R are matrices with elements in $Z_q$, that is elements are integers of at most q and q is derived from the security parameter, k and the upper bound on the size of the stream, n.
	So a rough estimate of the size of L and R can be calculated by multiplying the dimensions of the matrices, by the amount of space required for each element.
	Below are two tables of estimations.

@@

	The estimated memory footprint of the public key matrices grows rapidly with an increasing security parameter, but slowly with increasing stream size.
	The reason for this is that the scheme calls for matrices of size $k  \times ( k \times \log q )$.
	The matrix size grows faster than $k^2$ because $q$ also depends on $k$.
	Fortunately, the current proposal is to pick one security parameter which is large enough to provide the appropriate security properties for all instances of the SADS scheme.

	Future benchmarking efforts will also measure the memory footprint of the prover over time, and the size of a proof for varying parameter sizes. Additionally, we will benchmark the time required to perform the important updating and proof tasks for each of the prover and verifier.

	\subsection{ Production Quality Libraries }

	Through our benchmarking and profiling efforts, we hope to identify and fix the bottlenecks in implementation resulting in faster and higher quality code.
	We recognize that the built-in implementations of certain high cost operations, such as matrix multiplication may end up being the limiting factor, and as such we've identified a few options for future optimization.
	We hesitate to invest time and effort into any of these options too soon as we know that our first-draft implementation necessarily has room for improvement, but we outline those options here.

	\begin{enumerate}
	\item \textbf{SciRuby} : A Ruby library providing efficient implementations of linear algebra operations as well as other science, engineering, and visualization packages. \texttt{http://sciruby.com/}
	\item \textbf{NTL 5.5.2} : A free software written in C++ providing data structures and algorithms for arbitrary length integers, for vectors, matrices and polynomials over the integers and over the finite fields and for arbitrary precision floating point arithmetic. \texttt{http://shoup.net/ntl/}
	\item \textbf{MAGMA V2.18} : The kernel of Magma contains implementations of many of the important concrete classes of structure in five fundamental branches of algebra, namely group theory, ring theory, field theory, module theory and the theory of algebras.
	In addition, certain families of structures from algebraic geometry and finite incidence geometry are included. \texttt{http://magma.maths.usyd.edu.au/}
	\end{enumerate}
